Target Markdown

### 2022-08-24 _targets.Rmd
Further updates in Propensity score matching script (added new variable of "interdisciplinarity/specialisation" and "career age of receving first grant". Futher, all edidks that were not paired with any supervisor vedidk were deleted from the treatment sample

    # tar_target(one_author,
    #           read.csv2(here::here("data", "raw",    #"Binter_pubs.csv")),
 #              format = "qs"),
      tar_target(ids, read.csv2(here::here("data", "raw", "supervisors.csv"), nrows = 20),
              format = "qs"),
      tar_target(ids_complete, create_ids_complete(ids),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete)),
    tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
    tar_target(all_pubs,
           get_all_pubs(db_path, ids_complete), 
              format = "qs"),
    tar_target(one_author,
           read_one_author(db_path, ids_complete_vector, ids_complete), 
              format = "qs", pattern = map(ids_complete_vector), iteration = "list")

>>>>

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path, nrows = 20),
              format = "qs"),
      tar_target(ids_complete, create_ids_complete(ids),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete)),
    tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
    tar_target(all_pubs,
           get_all_pubs(db_path, ids_complete), 
              format = "qs"),
    tar_target(one_author,
           read_one_author(db_path, ids_complete_vector, ids_complete), 
              format = "qs", pattern = map(ids_complete_vector), iteration = "list")
